brados: declarative, programmable object storage

### 2016-05-25 paper.tex

\begin{table}[h]
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{3}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & EX  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system.}
\label{tab:pd-map}
\end{table}

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel_v_firefly_v_es.png}
	\caption{The cluster-specific optimizations impact performance... a lot. This caption is quite terrible.
	\label{fig:jewel_v_firefly_v_es}}
\end{figure*}

The top row of Figure~\ref{fig:jewel_v_firefly_v_es} shows the expected
performance of different sized log appends without metadata management overhead
using each of the five strategies defined in Table~\ref{tab:pd-map}.  Starting
with Jewel and 4KB entry sizes, we see that both one-to-one strategies have
relatively poor performance. Jewel with 1KB entry sizes sees a 2.5\(\times\)
performance increase for the \texttt{(N:1,KV)} mapping. The large period of reduced
throughput for corresponds to the OSD splitting file system directories in
order to maintain a maximum directory size, and will occur in \texttt{(1:1, KV)}
although the threshold number of objects is not reached in this example due to
the reduced overall throughput of the \texttt{(1:1, KV)} strategy.

@@

\begin{figure}[t]
      \centering
      \includegraphics[width=0.85\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
      \caption{The expected random read performance from a log with 1KB entries
      performs best on the same strategy that the writes perform
      best on - the \texttt{(N:1, BS)} append strategy.}
      \label{fig:vanilla_rd_jewel}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}	
	\caption{1hr,1k,cls\_wr,jewel: this graph shows the overhead of class}
	\label{fig:cls_wr_jewel}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel-hdd-128b.png}
	\caption{shows that with a HDD, it don't matter if you choose omap!!!!!}
	\label{fig:jewel-hdd-128b}
\end{figure}

@@

This physical design process, of first thinking about the design trade-offs and
then doing parameters sweeps, is insufficient for large general-purpose systems
like Ceph. Had we built ZLog from the ground up (like CORFU) the story might be
different but to deal with the large state space we need a way to automatically
and autonomically decide which parameters to choose.

>>>>

\begin{table}[h]
\begin{tabular}{ | l | l | l | l | l |}
\hline
Map & I/O & Entry Size & Addressing & Metadata \\ \hline
\multirow{3}{*}{1:1} & KV  & Flex     & Ceph      & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & Ceph/VFS  & KV/BS \\ \hline
\multirow{4}{*}{N:1} & KV  & Flex     & \multicolumn{2}{|c|}{KV/BS} \\ \cline{2-5}
                     & EX  & Fixed    & VFS       & KV/BS \\ \cline{2-5}
                     & AP  & Flex     & KV/BS     & KV/BS \\
\hline
\end{tabular}
\caption{The high-level design space of mapping CORFU log entry storage onto
the RADOS object storage system. }
\label{tab:pd-map}
\end{table}

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel_v_firefly_v_es.png}
	\caption{The relative performance difference between the different mapping strategies in Table~\ref{tab:pd-map} changes with the Ceph version. These discrepancies alter the implementation that a developer \emph{would have chosen} had they been developing on a different release. Here we vary the log entry size to show that there is a trend for Jewel (larger entry sizes decreases \texttt{(N:1)}'s relative performance) that is not present in Firefly.
	\label{fig:jewel_v_firefly_v_es}}
\end{figure*}

The top row of Figure~\ref{fig:jewel_v_firefly_v_es} shows the expected
performance of different sized log appends without metadata management overhead
using each of the five strategies defined in Table~\ref{tab:pd-map}.  Starting
with Jewel and 4KB entry sizes, we see that both one-to-one strategies have
relatively poor performance. Jewel with 1KB entry sizes sees a 2.5\(\times\)
performance increase for the \texttt{(N:1,KV)} mapping. The large period of reduced
throughput for corresponds to the OSD splitting file system directories in
order to maintain a maximum directory size, and will occur in \texttt{(1:1,KV)}
although the threshold number of objects is not reached in this example due to
the reduced overall throughput of the \texttt{(1:1,KV)} strategy.

@@

\begin{figure}[t]
      \centering
      \includegraphics[width=0.85\linewidth]{experiments/basic-cls-rand-read/output.read.60min.1k.png}
      \caption{The expected random read performance for a log with 1KB entries
      performs best on the same strategy that the writes perform
      best on - \texttt{(N:1, BS)}.}
      \label{fig:vanilla_rd_jewel}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}	
	\caption{The overhead of Ceph's object class interfaces and the cost of checking metadata affect the performance of the CORFU API on RADOS. The performance degradation of \texttt{KV} might not be enough to offset the simplicity of the implementation.}
	\label{fig:cls_wr_jewel}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=1.0\linewidth]{experiments/basic-cls-rand-read/jewel-hdd-128b.png}
	\caption{The performance of \texttt{(N:1,KV)} is within 1\% of \texttt{(N:1,BS)} when using the Ceph Jewel release on a HDD. For this specific hardware/software configuration, \texttt{(N:1,KV)} is a better implementation.}
	\label{fig:jewel-hdd-128b}
\end{figure}

@@

This physical design process, of first thinking about the design trade-offs and
then doing parameters sweeps, is insufficient for large general-purpose systems
like Ceph. Had we built CORFU from the ground up the story might be
different but to deal with the large state space we need a way to automatically
and autonomically decide which parameters to choose.
